---
title: "Chap6"
author: "Anjali Krishnan and Richard Troise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(xtable)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. **User will also input desired variable names in double quotes**
```{r}
data <- read.csv("chap6.csv", header = FALSE, skip = 1)
colnames(data) <- c("Expt", "Control")
```

We now combine the observations into one long column (score)
```{r}
colnames(data) <- c("V1", "V2")
score=c(data$V1,data$V2)
```

We generate a second column (levels), that identifies the group for each score. **User will also input desired variable names in double quotes**
```{r}
levels=factor(c(rep("Expt",5),rep("Control",5)))
```

We now use the means of the respective groups as the predictors
```{r}
Predictors=c(rep(mean(data$V1),5),rep(mean(data$V2),5))
```

We now form a data frame for the Regression approach, and print the results
```{r}
data_reg=data.frame(Predictors,score)
r=cor(Predictors,score)
knitr::kable(xtable(data_reg))
print(r)
```

Now we perform the regression analysis on the data
```{r}
reg1=lm(score~Predictors)
```

We now form a data frame with the dependent variable and the factors, then print the table.
```{r}
data=data.frame(score=score,group=levels)
knitr::kable(xtable(data))
```

We now generate the ANOVA table and regression analysis based on the linear model
```{r}
aov1=aov(score~levels)
print(model.tables(aov(score~levels),type = "means"),digits=3)
summary(aov1)
summary(reg1)
```

