---
title: "Chap1"
author: "Anjali Krishnan and Richard Troise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(dplyr)
library(xtable)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. User will also input desired variable names in double quotes
```{r}
data <- read.csv("chap1.csv", header = FALSE, skip = 1)
colnames(data) = c("Length", "Width")
```

View the data.
```{r}
knitr::kable(xtable(data))
```

Calculate the mean for all columns
```{r}
summarise_all(data,mean)
```

Calculate the standard deviation for all columns
```{r}
summarise_all(data,sd)
```


Replace 'var1' and 'var2' to an appropriate first and second column name using CTRL+F. **Only check off 'Match case' to avoid overwriting additional code.** 
```{r}
column = colnames(data)
colnames(data) <- c("V1", "V2")
var1 = data$V1
var2 = data$V2
```

We now perform a correlation and a test on the data which gives
confidence intervals, regression analysis on the data, an ANOVA on the data. Replace 'var1' and 'var2' to an appropriate first and second column names using CTRL+F
```{r}
cor1=cor.test(var1,var2, method = c("pearson"))
reg1=lm(var1~var2)
aov1=aov(var1~var2)
```

We now print the data and all the results. Adjust title before plotting in double quotes
```{r, fig.align='left'}
plot(data, main = "Length vs Meanings", 
     xlab = column[1], ylab = column[2], pch = 16)
```

Extracting the correlation test data. Nothing needs to be adjusted.
```{r}
cor_table = data.frame(df = cor1$parameter, 
                       t_value = cor1$statistic, 
                       p_value = cor1$p.value, 
                       r = cor1$estimate, 
                       LowC.I. = cor1$conf.int[1], 
                       UpperC.I = cor1$conf.int[2])

rownames(cor_table) = ""
```

Correlation Test
```{r}
knitr::kable(xtable(cor_table))
```

Regression Analysis
```{r}
summary(reg1)
```

ANOVA table
```{r}
summary(aov1)
```

