---
title: "Chap11_3"
author: "Anjali Krishnan and Richard Troise"
date: "5/27/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xtable)
library(gmodels)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. **User will also input desired variable names in double quotes**
```{r}
data <- read.csv("chap11_3.csv", header = FALSE, skip = 1)
colnames(data) <- c("sub_1", "sub_2", "sub_3", "sub_4", "sub_5", "sub_6", "sub_7", "sub_8")
```

We now combine the observations into one long column (score)
```{r}
colnames(data) <- c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8")
score=c(data$V1,data$V2,data$V3,data$V4,data$V5,data$V6,data$V7,data$V8)
```

We now prepare the labels for the 6x8 scores according to the
factor levels:
rank_1 rank_2 rank_3 rank_4 rank_5 rank_6........etc for
Factor A
```{r}
Rank=gl(6,1,8*6*1, labels = c("rank_1", "rank_2", "rank_3", "rank4", "rank_5", "rank_6"))
```

sub_1 sub_1......., sub_2 sub_2......,sub_3 sub_3 ....,sub_4
sub_4 ....., sub_5 sub_5....., sub_6 sub_6 etc for Subjects.
```{r}
Subject=gl(8,6*1,8*6*1, labels=c("sub _1", "sub_2", "sub_3",
                                 "sub_4", "sub_5", "sub_6", "sub_7", "sub_8"))
```

We now form a data frame with the dependent variable and the factors, then we print the results
```{r}
data = data.frame(score = score, Rank = factor(Rank), Subject =
                    factor(Subject))
knitr::kable(xtable(data))
```

Anova when "Subject" is considered as a random factor, then we print the results
```{r}
aov1=aov(score~Rank+Error(Subject),data=data)
summary(aov1)
print(model.tables(aov(score ~ Rank + Subject, data =
                         data),"means"),digits=3)
```

