---
title: "Chap4"
author: "Anjali Krishnan and Richard Troise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(dplyr)
library(ppcor)
library(xtable)
```

First, set working directory. 'data' is a table with three columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. **User will also input desired variable names in double quotes**
```{r}
data <- read.csv("chap4.csv", header = FALSE, skip = 1)
colnames(data) = c("Age", "SpeechRate", "CorrectRecall")
```

View the data.
```{r}
knitr::kable(xtable(data))
```

Calculate the mean for all columns
```{r}
summarise_all(data,mean)
```

Calculate the standard deviation for all columns
```{r}
summarise_all(data,sd)
```

Replace 'var1', 'var2', and 'var3' to an appropriate first, second, and third column name using CTRL+F. **Only check off 'Match case' to avoid overwriting additional code.**
```{r}
column = colnames(data)
colnames(data) <- c("V1", "V2", "V3")
var1 = data$V1
var2 = data$V2
var3 = data$V3
```

We now perform an orthogonal multiple regression analysis on the data
```{r}
multi_reg1=lm(var3~var1+var2,data=data)
```

We now compute the predicted values and the residuals, then print the results on a single table. Replace 'var3', the dependent variable, to an appropriate column name using CTRL+F. **Only check off 'Match case' to avoid overwriting additional code.**
```{r}
Y_hat=predict(multi_reg1)
Residual=round(residuals(multi_reg1),2)
knitr::kable(xtable(data.frame(Y=var3,Y_hat,Residual)))
```

We now compute the sum of squares of the residuals, then print the result
```{r}
SS_residual=sum(Residual^2)
print(SS_residual)
```

We now compute the correlation matrix between the variables. **User will also input desired variable names in double quotes**
```{r}
colnames(data) = c("Age", "SpeechRate", "CorrectRecall")
r_mat=cor(data)
Corr=round(r_mat,4)
knitr::kable(xtable((Corr)))
```

We now compute the semi-partial coefficients, then print the results. Replace 'var1', 'var2', and 'var3' to an appropriate first, second, and third column name using CTRL+F. **Only check off 'Match case' to avoid overwriting additional code.**
```{r}
colnames(data) <- c("V1", "V2", "V3")
var1 = data$V1
var2 = data$V2
var3 = data$V3
semi_r = spcor(data)
semi_part=data.frame(var1=semi_r$estimate[3,1]^2, var2=semi_r$estimate[3,2]^2)
knitr::kable(xtable((semi_part)))
```

Plotting the semi-partial correlations
```{r}
colnames(data) = c("var1", "var2", "var3")
semi_r = spcor(data)
barplot(semi_r$estimate, beside=TRUE, horiz=TRUE, 
        col=c("red","black","blue"),
        xlab="Semi-Partial Person r", xlim=c(-1,1))
legend("bottomleft", legend=c("var1","var2","var3"), fill=c("red","black","blue"))
```

Multi-Regression Analysis
```{r}
print(summary(multi_reg1))
```

ANOVA analysis
```{r}
print(anova(multi_reg1))
```


