---
title: "Chap11"
author: "Anjali Krishnan and Richard Troise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xtable)
library(gmodels)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. **User will also input desired variable names in double quotes**
```{r}
data <- read.csv("chap11.csv", header = FALSE, skip = 1)
colnames(data) <- c("sub_1", "sub_2", "sub_3", "sub_4", "sub_5")
```

We now combine the observations into one long column (score)
```{r}
colnames(data) <- c("V1", "V2", "V3", "V4", "V5")
score=c(data$V1,data$V2,data$V3,data$V4,data$V5)
```

We now prepare the labels for the 4x5 scores according to the
factor levels:
a1 a2 a3 a4, a1 a2 a3 a4........etc for Factor A
```{r}
Fact_A=gl(4,1,4*5*1, labels=c("a1","a2","a3","a4"))
```

sub_1 sub_1......., sub_2 sub_2......,sub_3 sub_3 ....,sub_4
sub_4 ....., sub_5 sub_5.....etc for Subjects
```{r}
Subject=gl(5,4*1,5*4*1, labels=c("sub_1", "sub_2", "sub_3","sub_4", "sub_5"))
```

We now form a data frame with the dependent variable and the factors, then we print the results
```{r}
data=data.frame(score = score,Factor_A = factor(Fact_A),
                Subject = factor(Subject))
knitr::kable(xtable(data))
```

Anova when "Subject" is considered as a random factor, then we print the results
```{r}
aov1=aov(score~Fact_A+Error(Subject),data=data)
summary(aov1)
print(model.tables(aov(score~Fact_A+Subject),"means"))
```

