---
title: "Chap5_2"
author: "Anjali Krishnan and Richard Troise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(xtable)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables. **User will also input desired variable names in double quotes**
```{r}
data <- read.csv("chap5_2.csv", header = FALSE, skip = 1)
colnames(data) <- c("No_Cont", "Cont_before", "Cont_after", "Part_cont")
```

We now combine the observations into one long column (score)
```{r}
colnames(data) <- c("V1", "V2", "V3", "V4")
score=c(data$V1,data$V2,data$V3,data$V4)
```

We generate a second column (levels), that identifies the group for each score. **User will also input desired variable names in double quotes**
```{r}
levels=factor(c(rep("No_cont",5),rep("Cont_before",5),
                rep("Cont_after",5),rep("Part_cont",5)))
```

We now form a data frame with the dependent variable and the factors, then print the table.
```{r}
data=data.frame(score=score,group=levels)
knitr::kable(xtable(data))
```

We now generate the ANOVA table based on the linear model
```{r}
aov1=aov(score~levels)
print(model.tables(aov(score~levels),type = "means"),digits=3)
summary(aov1)
```

