---
title: "Chap1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(dplyr)
library(xtable)
```

First, set working directory. 'data' is a table with two columns and same number of rows, and should be numeric. Columns have headers indicating the names of the variables.
```{r, echo=FALSE}
data <- read.csv("chap1.csv")
```

View the data
```{r}
data
```

Calculate the mean for all columns
```{r, echo=FALSE}
summarise_all(data,mean)
```

Calculate the standard deviation for all columns
```{r, echo=FALSE}
summarise_all(data,sd)
```

```{r, echo=FALSE}
rm(data)
```

```{r, echo=FALSE}
data <- read.csv("chap1.csv", header = FALSE, skip = 1)
Length = data$V1
Meaning = data$V2
```

We now perform a correlation and a test on the data which gives
confidence intervals, regression analysis on the data, an ANOVA on the data
```{r, echo=FALSE}
cor1=cor.test(Length, Meaning,method = c("pearson"))
reg1=lm(Length~Meaning)
aov1=aov(Length~Meaning)
```

We now print the data and all the results
```{r, echo=FALSE, fig.align='left'}
plot(data, main = "Length vs Meanings", xlab = "Length", ylab = "Meaning")
```

```{r, echo=FALSE}
cor_table = data.frame(df = cor1$parameter, 
                       t = cor1$statistic, 
                       p = cor1$p.value, 
                       r = cor1$estimate, 
                       LowC.I. = cor1$conf.int[1], 
                       UpperC.I = cor1$conf.int[2]) 
#print(cor1)
knitr::kable(xtable((cor_table)))
```

Regression Analysis
```{r, echo=FALSE}
knitr::kable(xtable(summary(reg1)))
```

ANOVA table
```{r, echo=FALSE}
knitr::kable(xtable((summary(aov1))))
```

